UKB Models

### 2023-10-12 ukb_curation-eda.Rmd
reorg data

```{r}
ukb_df_age.filt <- ukb_df_totals %>%
  dplyr::filter(age_yrs >= 50 & age_yrs <= 80)
#write data
write_csv(ukb_df_age.filt, file="data/ukb_CN_data_agefilt.csv")
```

@@

#write out
write_csv(ukb_df_sites, file="data/ukb_CN_data_simsites.csv")
```

>>>>

```{r}
ukb_df_age.filt <- ukb_df_totals %>%
  dplyr::filter(age_yrs >= 50 & age_yrs <= 80)
# #write data
# write_csv(ukb_df_age.filt, file="data/ukb_CN_data_agefilt.csv")
```

@@

#write out
write_csv(ukb_df_sites, file="data/ukb_to_model/ukb_CN_data_simsites.csv")
```
